K8S RESOURCE\\ SHARING

### 2019-10-01 openinfranordics2019/presentation.tex
Add slides for openinfra day nordic

\usepackage[utf8]{inputenc}
\usepackage[russian, english]{babel}
\usepackage{booktabs}
\usepackage[scale=2]{ccicons}
\usepackage{listings}
\usepackage{marvosym}
\usepackage{color}
\usepackage{xcolor}
\usepackage[document]{ragged2e}
\usepackage[export]{adjustbox}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{minted}
\usemintedstyle{tango}
\usepackage[normalem]{ulem}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usetikzlibrary{mindmap}
\usetikzlibrary{shapes.misc, fit}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{verbatim}
\usepackage{smartdiagram}
\usesmartdiagramlibrary{additions}
\usetikzlibrary{trees}
\usepackage{datetime}
\usepackage{hyperref}

@@

    \begin{tikzpicture}[]

@@

        \draw \firstcircle node [below] {\textbf{res}};
        \draw \secondcircle node [above] {\textbf{limit}};
        \draw \thirdcircle node [below] {\textbf{time}};
    \end{scope}
    \end{tikzpicture}

@@

                \begin{itemize}[label={\MVRightarrow}]
                    \item<+-> classic
                    \item<+-> transparent
                    \item<+-> isolation only per pod
                    \item<+-> no soft limits or reclaim (SIGBUS)
                \end{itemize}
            \end{center}
        \end{column}

@@

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \textbf{Huge pages}

@@

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \textbf{LLCache}

        \begin{flushleft}
		\begin{minted}[fontsize=\normalsize]{bash}
=> pqos -s
L3CA COS definitions for Socket 0:
	L3CA COS0 => MASK 0xffff
	L3CA COS1 => MASK 0xf
	L3CA COS2 => MASK 0xff0
	L3CA COS3 => MASK 0xfff
Core information for socket 0:
	Core 0, L2ID 0, L3ID 0 => COS0
	Core 1, L2ID 1, L3ID 0 => COS0
	Core 2, L2ID 0, L3ID 0 => COS0
	Core 3, L2ID 1, L3ID 0 => COS0
        \end{minted}
        \end{flushleft}

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \textbf{LLCache}

        \begin{flushleft}
		\begin{minted}[fontsize=\normalsize]{bash}
# COS1 4 cache ways, COS 2 next 8 cache ways
=> pqos -e "llc:1=0x000f;llc:2=0x0ff0;"
SOCKET 0 L3CA COS1 => MASK 0xf
SOCKET 0 L3CA COS2 => MASK 0xff0
Allocation configuration altered.
        \end{minted}
        \end{flushleft}

@@

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \textbf{Network}

        \begin{itemize}[label={\MVRightarrow}]
			\item vlanx
            \item network class
            \item traffic control
        \end{itemize}

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \textbf{Noise}

        \begin{itemize}[label={\MVRightarrow}]
			\item Futex
            \item Compaction
            \item Readahead
            \item Filesystem
            \item ...
        \end{itemize}

    \end{center}
\end{frame}
\note {
    readahead for io congested cgroups is not happen
}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[russian, english]{babel}
\usepackage{booktabs}
\usepackage[scale=2]{ccicons}
\usepackage{listings}
\usepackage{marvosym}
\usepackage{color}
\usepackage{xcolor}
\usepackage[document]{ragged2e}
\usepackage[export]{adjustbox}
\usepackage{fontawesome}
\usepackage{enumitem}
\usepackage{minted}
\usemintedstyle{tango}
\usepackage[normalem]{ulem}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usetikzlibrary{mindmap}
\usetikzlibrary{shapes.misc, fit}
\usepackage{graphicx}
\usepackage{eso-pic}
\usepackage{verbatim}
\usepackage{smartdiagram}
\usesmartdiagramlibrary{additions}
\usetikzlibrary{trees}
\usepackage{datetime}
\usepackage{hyperref}
\usepackage[normalem]{ulem}

@@

\begin{frame}[fragile]{}
    \frametitle{}

    \only<1>{
        \begin{center}
        \begin{tikzpicture}[]

        \def\firstcircle{(0,0) circle (1.5cm)}
        \def\secondcircle{(60:4cm) circle (1.5cm)}
        \def\thirdcircle{(0:4cm) circle (1.5cm)}

            \draw \firstcircle node [] {\textbf{res}};
            \draw \secondcircle node [] {\textbf{limit}};
            \draw \thirdcircle node [] {\textbf{time}};
        \end{scope}
        \end{tikzpicture}
        \end{center}
    }

    \only<2> {
        \begin{center}
        \begin{tikzpicture}[]

@@

            \draw \firstcircle node [below] {\textbf{res}};
            \draw \secondcircle node [above] {\textbf{limit}};
            \draw \thirdcircle node [below] {\textbf{time}};
        \end{scope}
        \end{tikzpicture}
        \end{center}
    }

@@

                \begin{itemize}[label={\MVRightarrow}]
                    \item classic
                    \item \sout{transparent}
                    \item isolation only per pod
                    \item no soft limits or reclaim (SIGBUS)
                \end{itemize}
            \end{center}
        \end{column}

@@

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{center}
        \textbf{Huge pages experiment}

@@

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{columns}
        \begin{column}{0.48\columnwidth}
        \begin{minted}[fontsize=\normalsize]{yaml}

    resources:
      requests:
        cpu: "1000m"
        memory: "1GB"
        hugepages-1Gi: "1GB"
        hugepages-2Mi: "1GB"
      limits:
        cpu: "2000m"
        memory: "2GB"
        hugepages-1Gi: "2GB"
        hugepages-2Mi: "2GB"
        \end{minted}
        \end{column}

        \begin{column}{0.48\columnwidth}
            \vspace*{-2.5em}
            \begin{center}
            \fontsize{28pt}{30}\selectfont{\color{black} \textbf{What is missing?}}
            \end{center}
        \end{column}

\begin{frame}[fragile]{}
    \frametitle{}
    \begin{columns}
        \begin{column}{0.48\columnwidth}
        \begin{minted}[fontsize=\normalsize]{yaml}

    resources:
      requests:
        cpu: "1000m"
        memory: "1GB"
        hugepages-1Gi: "1GB"
        hugepages-2Mi: "1GB"
      limits:
        cpu: "2000m"
        memory: "2GB"
        hugepages-1Gi: "2GB"
        hugepages-2Mi: "2GB"
        \end{minted}
        \end{column}

        \begin{column}{0.48\columnwidth}
            \begin{center}
            \begin{minted}[fontsize=\normalsize]{yaml}
resources:
  requests:
    io: "?"
    llcache: "?"
    network: "?"

  limits:
    io: "?"
    llcache: "?"
    network: "?"

            \end{minted}
            \end{center}
        \end{column}

%\begin{frame}[fragile]{}
    %\frametitle{}
    %\begin{center}
        %\textbf{LLCache}

        %\begin{flushleft}
		%\begin{minted}[fontsize=\normalsize]{bash}
%=> pqos -s
%L3CA COS definitions for Socket 0:
	%L3CA COS0 => MASK 0xffff
	%L3CA COS1 => MASK 0xf
	%L3CA COS2 => MASK 0xff0
	%L3CA COS3 => MASK 0xfff
%Core information for socket 0:
	%Core 0, L2ID 0, L3ID 0 => COS0
	%Core 1, L2ID 1, L3ID 0 => COS0
	%Core 2, L2ID 0, L3ID 0 => COS0
	%Core 3, L2ID 1, L3ID 0 => COS0
        %\end{minted}
        %\end{flushleft}

    %\end{center}
%\end{frame}

%\begin{frame}[fragile]{}
    %\frametitle{}
    %\begin{center}
        %\textbf{LLCache}

        %\begin{flushleft}
		%\begin{minted}[fontsize=\normalsize]{bash}
%# COS1 4 cache ways, COS 2 next 8 cache ways
%=> pqos -e "llc:1=0x000f;llc:2=0x0ff0;"
%SOCKET 0 L3CA COS1 => MASK 0xf
%SOCKET 0 L3CA COS2 => MASK 0xff0
%Allocation configuration altered.
        %\end{minted}
        %\end{flushleft}

    %\end{center}
%\end{frame}

@@

%\begin{frame}[fragile]{}
    %\frametitle{}
    %\begin{center}
        %\textbf{Network}

        %\begin{itemize}[label={\MVRightarrow}]
			%\item vlanx
            %\item network class
            %\item traffic control
        %\end{itemize}

    %\end{center}
%\end{frame}

%\begin{frame}[fragile]{}
    %\frametitle{}
    %\begin{center}
        %\textbf{Noise}

        %\begin{itemize}[label={\MVRightarrow}]
			%\item Futex
            %\item Compaction
            %\item Readahead
            %\item Filesystem
            %\item ...
        %\end{itemize}

    %\end{center}
%\end{frame}
%\note {
    %readahead for io congested cgroups is not happen
%}
